Solar wind discontinuities spatial evolution in the outer heliosphere

### 2024-02-02 _tex/index.tex
Built site for gh-pages

\section{Methods}\label{methods}

\begin{itemize}
\tightlist
\item
  We use \citep{liuMagneticDiscontinuitiesSolar2022} method to identify IDs, which has better compatibility for the IDs with minor field changes.
\item
  Then the minimum variance analysis is applied to each ID event to obtain the boundary normal (LMN) coordinate and extract IDs' features.
\end{itemize}

@@

@@

>>>>

\section{Dataset, models, and methods}\label{dataset-models-and-methods}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1220}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0976}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1402}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1159}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1280}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.3963}}@{}}

\caption{\label{tbl-missions}Missions info}

\tabularnewline

\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Mission
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\(\delta t_B\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\(\delta t_{plasma}\)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Radial coverage
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Launch date
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
website
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Juno & 1 Hz & & 1 - 5.5 AU & 2011-08-05 00:00:00 &
{[}`\href{https://science.nasa.gov/mission/juno}{NASA}'{]} \\
ARTEMIS & 5 Hz, \ldots{} & & & 2007-02-17 00:00:00 & \\
STEREO-A & 8 Hz & & & 2006-10-26 00:00:00 & \\
WIND & 11 Hz & & & 1994-11-01 00:00:00 &
{[}`\href{https://science.nasa.gov/mission/wind/}{NASA}'{]} \\
Solar Orbiter & & & 0.28 - 0.9 AU & 2020-02-10 00:00:00 &
{[}`\href{https://sci.esa.int/web/solar-orbiter}{ESA}'{]} \\
Parker Solar Probe & & & 0.05 - 1 AU & 2018-08-12 00:00:00 &
{[}`\href{https://science.nasa.gov/mission/parker-solar-probe}{NASA}'{]} \\

\end{longtable}

\textsubscript{Source: \href{https://Beforerr.github.io/ids_spatial_evolution_juno/notes.ipynb.html\#cell-tbl-missions}{Notes}}

\subsection{Methods}\label{methods}

We will use Liu's \citep{liu2022a} method to identify discontinuities in the solar wind. This method has better compatibility for the discontinuities with minor field changes, and is more robust to the situation encountered in the outer heliosphere. For each sampling instant \(t\), we define three intervals: the pre-interval \([-1,-1/2]\cdot T+t\), the middle interval \([-1/,1/2]\cdot T+t\), and the post-interval \([1/2,1]\cdot T+t\), in which \(T\) are time lags. Let time series of the magnetic field data in these three intervals are labeled \({\mathbf B}_-\), \({\mathbf B}_0\), \({\mathbf B}_+\), respectively. Then for an discontinuity, the following three conditions should be satisfied: (1) \(\sigma({\mathbf B}_0)>2\max\left(\sigma({\mathbf B}_-, \sigma({\mathbf B}_+)\right)\), (2) \(\sigma\left({\mathbf B}_-+{\mathbf B}_+\right)>\sigma({\mathbf B}_-)+\sigma({\mathbf B}_+)\), and (3) \(|\Delta {\mathbf B}|>|{\mathbf B}_{bg}|/10\), in which \(\sigma\) and \({\mathbf B}_{bg}\) represent the standard deviation and the background magnetic field magnitude, and \(\Delta {\mathbf B}={\mathbf B}(t+T/2)-{\mathbf B}(t-T/2)\). The first two conditions guarantee that the field changes of the discontinuity identified are large enough to be distinguished from the stochastic fluctuations on magnetic fields, while the third is a supplementary condition to reduce the uncertainty of recognition. We also will use the minimum or maximum variance analysis (MVA) analysis \citep{sonnerupMinimumMaximumVariance1998, sonnerupMagnetopauseStructureAttitude1967} to determine the main (most varying) magnetic field component, \(B_l\), and medium variation component, \(B_m\). Figure~\ref{fig-examples} shows several examples of solar wind discontinuities detected by different spacecraft.

@@

\begin{minipage}{0.25\linewidth}
\includegraphics{figures/examples/artemis_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/examples/stereo_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
\includegraphics{figures/examples/wind_id_example.pdf}\end{minipage}%
%
\begin{minipage}{0.25\linewidth}
Examples of IDs from ARTEMIS, STEREO, and Wind\end{minipage}%

@@

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/thickness/thickness_k_dist.pdf}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/thickness/thickness_k_N1_dist.pdf}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/thickness/thickness_k_N1_r_dist.pdf}\end{minipage}%

\begin{minipage}{0.50\linewidth}
\includegraphics{figures/current/current_k_dist.pdf}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics{figures/current/current_k_N1_dist.pdf}\end{minipage}%
